Share Buyback and Equity Issue Anomalies Revisited

### 2016-02-16 report.Rnw
tool update

<< eval = TRUE, echo=FALSE,message=FALSE,fig.pos='h',results='asis' >>=
#rm(list=ls()) # Clean up the memory, if we want to rerun from scratch
#dev.off();
#library(knitr); knit2pdf('bb_issuers.Rnw', texi2dvi='texi2dvi'); file.remove(paste("bb_issuers",c(".aux",".tex",".blg",".bbl",".log",".out"),sep=""))
#dir.create("tmpfiles") # need to comment this if the directory already exists

#load("tmpfiles/bb_issuersALL.Rdata")
reload_data = 0

@@

if (generate_rnw_data == 1){
  source("bb_issuers.R")
}  else{
  if (reload_data)
    load("tmpfiles/bb_issuersALL.Rdata")
  source("lib_helpers.R") 
  source("latex_code.R")
  source("dataset/indices_and_factors/ff_industries_sic.R")
  source("business_data_clean.R")
  source("Paper_global_parameters.R")
}

@@

@@

\begin{document}

@@

@@

colnames(ISS_for_BB_Abn_table)[1]<- "Post-buyback SEOs"
colnames(ISS_for_BB_Abn_table)[4]<- "Other SEOs"

@@

lastSpecial=T,
titleontop = T
)
@

@@

<<   eval = TRUE, echo=FALSE,message=FALSE,fig.pos='h',results='asis' >>=
one_table = cbind(BBtable_undertime[,7:12],BB_cal_table_undertime[,7:12],
                  BBtable_undertime[,19:24],BB_cal_table_undertime[,19:24],
                  BBtable_undertime[,31:36],BB_cal_table_undertime[,31:36],
                  BBtable_undertime[,43:48],BB_cal_table_undertime[,43:48]
)
#one_table = BBtable_undertime
printLatexTable(one_table[reported_times,1:12],
                columns = c("High U-index (IRATS)","Low U-index (IRATS)","High U-index (CAL)","Low U-index (CAL)"),
                rowcolumn="1985-1990",
                title="Buyback returns for the U-index over time",
                caption="The table presents the long-run abnormal returns for firms after open market repurchase announcements for high and low U-index firms in different time periods and shows significantly larger returns by buybacks announced by high U-index firms compared to those with a low U-index. We report both the IRATS cumulative average abnormal returns (CAR, Panel~A) and the calender time method (AR, Panel~B) abnormal returns on the full sample. $t$-Statistics are provided and stars indicate significance at the $5\\%$ (*), and $1\\%$ level (**). \\\\",
                label="tbl:PastFindingsTimeUnderBB",metric=c("CAR", "CAR", "AR", "AR"),
                scale = 1,close=F,lastSpecial=T
)
printLatexTable(one_table[reported_times,13:24],open=F,close=F,rowcolumn="1991-2000",columns = c("High U-index (IRATS)","Low U-index (IRATS)","High U-index (CAL)","Low U-index (CAL)"),metric=c("CAR", "CAR", "AR", "AR"),scale = 1,lastSpecial=T)
printLatexTable(one_table[reported_times,25:36],open=F,close=F,rowcolumn="2001-2014",columns = c("High U-index (IRATS)","Low U-index (IRATS)","High U-index (CAL)","Low U-index (CAL)"),metric=c("CAR", "CAR", "AR", "AR"),scale = 1,lastSpecial=T)
printLatexTable(one_table[reported_times,37:48],open=F,rowcolumn="2008-2014",columns = c("High U-index (IRATS)","Low U-index (IRATS)","High U-index (CAL)","Low U-index (CAL)"),metric=c("CAR", "CAR", "AR", "AR"),scale = 1,lastSpecial=T)

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%XXXXXXX NOW ALL FIGURES
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{figure}[H]
\centering
<<   fig.width=10, fig.height=7, out.width='\\textwidth', echo=F >>=
par(mfrow=c(2,1), mar=c(2.2,4.5,2.2,4.5))

@@

pnl_Exit_Hedged = BB_ISS_Exit_Hedged
pnl_NoExit_Hedged = BB_ISS_NoExit_Hedged
plot(cumsum(100*pnl_NoExit_Hedged),type="l",ylab="CAR", xlab = "",main = "Panel B: Strategy Returns", axes = FALSE, ylim=c(min(c(100*cumsum(pnl_NoExit_Hedged),cumsum(100*pnl_Exit_Hedged))), max(c(cumsum(100*pnl_NoExit_Hedged),cumsum(100*pnl_Exit_Hedged)))), cex.lab=1.1)
axis(1,at=seq(1,length(pnl_NoExit_Hedged),length.out=10),labels=str_sub(names(pnl_NoExit_Hedged)[seq(1,length(pnl_NoExit_Hedged),length.out=10)], start = 1, end=4),cex.axis=0.8,las=3)
axis(2,cex.axis=1.1)
lines(cumsum(100*pnl_Exit_Hedged), lty = 2,lwd=1.4)
for (iter in floor(100*min(c(cumsum(pnl_NoExit_Hedged),cumsum(pnl_Exit_Hedged)))/100):floor(100*max(c(cumsum(pnl_NoExit_Hedged),cumsum(pnl_Exit_Hedged)))/100))
  abline(h = 100*iter)
#plot_crisis_dates(pnl_NoExit_Hedged) 
legend(x="topleft",
       c("Without Exit","With Exit"),
       lty=c("solid","dashed"),
       lwd=c(2,2),
       cex=1,bg="white",inset=0.01)

@@

>>>>

<< eval = TRUE, echo=FALSE,message=FALSE,fig.pos='h',results='asis' >>=
#rm(list=ls()) # Clean up the memory, if we want to rerun from scratch
#dev.off();
#library(knitr); knit2pdf('report.Rnw', texi2dvi='texi2dvi'); file.remove(paste("report",c(".aux",".tex",".blg",".bbl",".log",".out"),sep=""))
#dir.create("tmpfiles") # need to comment this if the directory already exists

#Timing: 
require(tictoc)
tic() #without report_tool.R: 77s

###################################################
## SAME AS bb_issuers.Rnw
reload_data = 1

@@

if (generate_rnw_data == 1){
  source("bb_issuers.R")
}  else{
  if (reload_data)
    #load("tmpfiles/bb_issuersALL.Rdata")
    load("bb_issuersTOOL.Rdata")
  source("lib_helpers.R") 
  source("latex_code.R")
  source("dataset/indices_and_factors/ff_industries_sic.R")
  source("business_data_clean.R")
  source("Paper_global_parameters.R")
}

@@

########################################################################################################
## REPORT.RNW SPECIAL CODE:
########################################################################################################

#Add any/all choices made in the tool here
if(!exists("input")){
  input = list()
  input$startdate <- as.Date("2000-12-31")
  input$enddate <- as.Date("2014-12-31")
  input$market_cap_min = 50
  input$market_cap_max = 505755
  input$quantile_used_ind = 0.2
  input$quantile_used_all = 0.4

  #for extra sections
  input$characteristic_irats1 <- "BE.ME.Score"
  input$characteristic_irats1_sign <- T

  input$characteristic_irats2 <- "Pre.Vol.Score"
  input$characteristic_irats2_sign <- T
}

options(warn=-1) #because some period don't have data
source("report_helpers.R")
source("report_tool.R")
source("report_tool_section.R")
options(warn=0)

#Now overwrite any variables that need redefining
firstyear = as.character(format(input$startdate,"%Y"))
lastyear = as.character(format(input$enddate,"%Y"))
FirstTrade = input$startdate

@@

\begin{document}
%\SweaveOpts{concordance=TRUE}

@@

%########################################################################################################
%## REPORT.RNW SPECIAL CODE:
%########################################################################################################

\section{Additional Variables Exploration}
<< Generate extra sections, echo=F,eval=T,results='asis' >>=
#this cats the text but returns some tables to be place at the end
options(warn=-1) #because some period don't have data

sec1 <- generate_section(input$characteristic_irats1,input$characteristic_irats1_sign,input$quantile_used_ind)
sec2 <- generate_section(input$characteristic_irats2,input$characteristic_irats2_sign,input$quantile_used_ind)
sec3 <- generate_section(input$characteristic_irats3,input$characteristic_irats3_sign,input$quantile_used_ind)
sec4 <- generate_section(input$characteristic_irats4,input$characteristic_irats4_sign,input$quantile_used_ind)
sec5 <- generate_section(input$characteristic_irats5,input$characteristic_irats5_sign,input$quantile_used_ind)
sec6 <- generate_section(input$characteristic_irats6,input$characteristic_irats6_sign,input$quantile_used_ind)

secU <- generate_U_section(sec1,sec2,sec3,sec4,sec5,sec6, input$quantile_used_ind,input$quantile_used_all)
options(warn=0) #because some period don't have data

@
%########################################################################################################
%########################################################################################################

@@

if(! is.null(ISS_for_BB_Abn_table)) {
  colnames(ISS_for_BB_Abn_table)[1]<- "Post-buyback SEOs"
  colnames(ISS_for_BB_Abn_table)[4]<- "Other SEOs"

@@

  lastSpecial=T,
  titleontop = T
  )
} else {
  cat("\\begin{table}
  \\caption{Issue announcements with and without a prior buyback: not enough data to generate}
  \\label{tbl:BBISSexitAfter}
  \\end{table}
  ");
}
@

@@

<<   eval = TRUE, echo=FALSE,message=FALSE,fig.pos='h',results='asis' >>=
one_table = cbind(BBtable_undertime[reported_times,7:12],BB_cal_table_undertime[reported_times,7:12],
                  BBtable_undertime[reported_times,19:24],BB_cal_table_undertime[reported_times,19:24],
                  BBtable_undertime[reported_times,31:36],BB_cal_table_undertime[reported_times,31:36],
                  BBtable_undertime[reported_times,43:48],BB_cal_table_undertime[reported_times,43:48]
)
#one_table = BBtable_undertime
printLatexTable(one_table[,1:12],
                columns = c("High U-index (IRATS)","Low U-index (IRATS)","High U-index (CAL)","Low U-index (CAL)"),
                rowcolumn="1985-1990",
                title="Buyback returns for the U-index over time",
                caption="The table presents the long-run abnormal returns for firms after open market repurchase announcements for high and low U-index firms in different time periods and shows significantly larger returns by buybacks announced by high U-index firms compared to those with a low U-index. We report both the IRATS cumulative average abnormal returns (CAR, Panel~A) and the calender time method (AR, Panel~B) abnormal returns on the full sample. $t$-Statistics are provided and stars indicate significance at the $5\\%$ (*), and $1\\%$ level (**). \\\\",
                label="tbl:PastFindingsTimeUnderBB",metric=c("CAR", "CAR", "AR", "AR"),
                scale = 1,close=F,lastSpecial=T
)
printLatexTable(one_table[reported_times,13:24],open=F,close=F,rowcolumn="1991-2000",columns = c("High U-index (IRATS)","Low U-index (IRATS)","High U-index (CAL)","Low U-index (CAL)"),metric=c("CAR", "CAR", "AR", "AR"),scale = 1,lastSpecial=T)
printLatexTable(one_table[reported_times,25:36],open=F,close=F,rowcolumn="2001-2014",columns = c("High U-index (IRATS)","Low U-index (IRATS)","High U-index (CAL)","Low U-index (CAL)"),metric=c("CAR", "CAR", "AR", "AR"),scale = 1,lastSpecial=T)
printLatexTable(one_table[reported_times,37:48],open=F,rowcolumn="2008-2014",columns = c("High U-index (IRATS)","Low U-index (IRATS)","High U-index (CAL)","Low U-index (CAL)"),metric=c("CAR", "CAR", "AR", "AR"),scale = 1,lastSpecial=T)

@@

%########################################################################################################
%## REPORT.RNW SPECIAL CODE:
%########################################################################################################

<<  eval = TRUE, echo=FALSE,message=FALSE,fig.pos='h',results='asis' >>=
#cat all the tables for the individual variables
for(i in 1:6) {
  sec <- eval(parse(text=paste("sec",i,sep="")))
  if(!is.null(sec)) {
    cat(sec$car_table)
    cat(sec$under_table)
  }
}
#cat the U-index table and others
cat(secU$car_table)
cat(secU$CEU_IRATStable_bb_latex)
cat(secU$CEU_CALtable_bb_latex)

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Special table combining industry characteristics and High/Low of all additional variables
\small
<<  eval = TRUE, echo=FALSE,message=FALSE,fig.pos='h',results='asis' >>=
tmp = generate_industry_table(sec1,sec2,sec3,sec5,sec5,sec6)
latex_render_data_frame(
  round(tmp,1), 
  title = "Industry Characteristics",
  caption="Percentage of high and low subset companies for all industries for which we have at least 100 events in our sample.",
  label = "tbl:industriesAdditional",
  columns=NULL,
  bigtitleontop = T,
  show_rownames=TRUE,
  scale = 1,
  digits=1,
  lastSpecial=F,dorotate=T
)
@
\normalsize

<<  eval = TRUE, echo=FALSE,message=FALSE,fig.pos='h',results='asis' >>=
rownames(secU$Under_IdioBB2)[1:2] <- c("high U-index", "low U-index")
latex_render_data_frame(
  round(secU$Under_IdioBB2[1:6,1:4],1), 
  title = "Relations across firm characteristics for Buybacks",
  caption="Relation between Under/Overvaluation and High/Low samples of the additional variables for buybacks. Numbers indicate percentage of firms in the row that are also categorized as noted in the columns.",
  label = "tbl:underidioallBB2",
  columns=NULL,
  bigtitleontop = T,
  show_rownames=TRUE,
  scale = 0.9,
  digits=1,
  lastSpecial=F,dorotate=F
)

latex_render_data_frame(
  round(secU$Under_IdioBB_cor2,2), 
  title = "Correlations of Buybacks Characteristics",
  caption="Correlation between all of the buybacks characteristics considered and the U-index score. All scores are defined using the universe of all CRSP companies at the time of the announcement with data up to the month before the announcement.",
  label = "tbl:underidioallBBcor2",
  columns=NULL,
  bigtitleontop = T,
  show_rownames=TRUE,
  scale = 0.9,
  digits=2,
  lastSpecial=F,dorotate=F
)
@

%########################################################################################################
%## REPORT.RNW SPECIAL CODE ENDS HERE
%########################################################################################################

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%XXXXXXX NOW ALL FIGURES
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\clearpage
\begin{figure}[H]
\centering
<<   fig.width=10, fig.height=7, out.width='\\textwidth', echo=F >>=
par(mfrow=c(2,1), mar=c(2.2,4.5,2.2,4.5))

@@

pnl_Exit_Hedged = BB_ISS_Exit_Hedged
pnl_NoExit_Hedged = BB_ISS_NoExit_Hedged[(which(pnl_NoExit_Hedged!=0)[1]):(tail(which(pnl_NoExit_Hedged!=0),1))]
plot(cumsum(100*pnl_NoExit_Hedged),type="l",ylab="CAR", xlab = "",main = "Panel B: Strategy Returns", axes = FALSE, ylim=c(min(c(100*cumsum(pnl_NoExit_Hedged),cumsum(100*pnl_Exit_Hedged))), max(c(cumsum(100*pnl_NoExit_Hedged),cumsum(100*pnl_Exit_Hedged)))), cex.lab=1.1)

axis(1,at=seq(1,length(pnl_NoExit_Hedged),length.out=10),labels=str_sub(names(pnl_NoExit_Hedged)[seq(1,length(pnl_NoExit_Hedged),length.out=10)], start = 1, end=4),cex.axis=0.8,las=3)
axis(2,cex.axis=1.1)
lines(cumsum(100*pnl_Exit_Hedged), lty = 2,lwd=1.4)
for (iter in floor(100*min(c(cumsum(pnl_NoExit_Hedged),cumsum(pnl_Exit_Hedged)))/100):floor(100*max(c(cumsum(pnl_NoExit_Hedged),cumsum(pnl_Exit_Hedged)))/100))
  abline(h = 100*iter)
#plot_crisis_dates(pnl_NoExit_Hedged) 
legend(x="topleft",
       c("Without Exit","With Exit"),
       lty=c("solid","dashed"),
       lwd=c(2,2),
       cex=1,bg="white",inset=0.01)

@@

%########################################################################################################
%## REPORT.RNW SPECIAL CODE:
%########################################################################################################

\begin{figure}[H]
\centering
<< fig.width=10, fig.height=6, out.width='\\textwidth', echo=F >>=
IRATS_table_all_bb_plot = secU$CEU_IRATStable_bb
IRATS_table_all_bb_plot[rownames(IRATS_table_all_bb_plot) %in% as.character((-6):(-1)),which(colnames(IRATS_table_all_bb_plot)=="CAR")] <- -IRATS_table_all_bb_plot[rownames(IRATS_table_all_bb_plot) %in% as.character((-6):(-1)),which(colnames(IRATS_table_all_bb_plot)=="CAR")]

#plot maximal first
plot(IRATS_table_all_bb_plot[reported_times_plots,dim(IRATS_table_all_bb_plot)[2]-2], ylim = ylimit,axes=FALSE, type = "l", ylab = "CAR", xlab="Months",main="Buybacks - CEU index", lwd=1, lty = "solid")
axis(1,at=plot_tickers,labels=plot_xlabels,cex.axis=0.8,las=3)
axis(2,cex.axis=1.1)

#now others
linestyle  = c("solid","dotted","dotted","dashed","dashed","dotdash","solid")
withpoints = c(F,    F,        T      ,F       ,T       ,F        ,T      )

theindex = rev(1:(dim(IRATS_table_all_bb_plot)[2]/3))
for(i in 1:length(theindex)) {
  lines(IRATS_table_all_bb_plot[reported_times_plots,3*(theindex[i]-1)+1],lwd = 2, lty=linestyle[i])
  if(withpoints[i]) {
    tmp = IRATS_table_all_bb_plot[reported_times_plots,3*(theindex[i]-1)+1]
    tmp[c(3*(1:floor(length(tmp)/3)),3*(1:floor(length(tmp)/3))+1)] <- NA
    points(tmp, pch=23,lwd=1)
  }
}

pchs = withpoints[1:length(theindex)]
pchs[pchs] = 23
pchs[!pchs] = NA
legend(x="topleft",
       title="CEU index value",
       legend = theindex,
       lty=linestyle[1:length(theindex)],
       lwd=(1:length(theindex))*0+2,
       pch=pchs,
       cex=1,bg="white",inset=0.01)
@
\caption{Long-run IRATS five factors cumulative abnormal returns of buybacks depending on the CEU-index. From the highest to the lowest lines as indicated by the legend. The x-axis indicates months from the date of the event announcement.}
\label{fig:CEpastall}
\end{figure}

This document took \Sexpr{toc()$tic/1000} seconds to produce.
%########################################################################################################
%## REPORT.RNW SPECIAL CODE ENDS HERE
%########################################################################################################
